Verifying Demonstrations

### 2018-08-28 paper/timestamp.tex
Minor clarifications in timestamping

We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), \(\TSstamp\) and \(\TStime\) such that
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to 1\) and \(\TStime[\pi] = t\).
\end{itemize}

@@

Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land \TStime[\pi_{t_1}] = t_1\).

>>>>

We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), 
\(\TSstamp\) and \(\TStime\) such that
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
    \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

@@

Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
  \TStime[\pi_{t_1}] = t_1\).
